\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage[hidelinks]{hyperref}
\newcommand*{\Comb}[2]{{}_{#1}C_{#2}}%

\usepackage{tabularx,ragged2e}
\newcolumntype{C}{>{\Centering\arraybackslash}X} % centered "X" column
% \newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}

\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Primi Composti: a Tabletop Game Analysis}

\author{
\IEEEauthorblockN{1\textsuperscript{st} Lorenzo Serafini}
\IEEEauthorblockA{
\textit{University Of Padua}\\
Padua, Italy \\
lorenzo.serafini.1@studenti.unipd.it}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Michele Sprocatti}
\IEEEauthorblockA{
\textit{University Of Padua}\\
Padua, Italy \\
michele.sprocatti@studenti.unipd.it \\ https://orcid.org/0009-0005-7886-441X}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Riccardo Zuech}
\IEEEauthorblockA{
\textit{University Of Padua}\\
Padua, Italy \\
riccardo.zuech@studenti.unipd.it}
}
\maketitle

\begin{abstract}
	This project has the objective of providing a game theoretic analysis of a real-world scenario, that is the tabletop game Primi Composti. In particular, we are interested in checking whether there is an inherent advantage in going first or second by considering all combinations of different practical strategies from a set we define.
	This project tackles some of the challenges that arise when applying game theoretic tools to real-world practical scenarios, like dealing with the random assignments of cards to the players and the high computational costs of standard best-response strategies. So in order to deal with these aspects, we have tried to find a balance over the number of samples and the number of strategies in order to have statistical significance and also to not have too much computational time required to run all the computations.
    After the simulations, some analyses are performed in order to understand if there are some advantages and if the game is fair enough for both players.
    Finally a minimization method is used to find the best binomial distribution that best fits the data resulting by the simulations.
\end{abstract}

\input{sections/Introduction}
\input{sections/Strategies}
\input{sections/Simulation2}
%\input{sections/Simulation}
\input{sections/Conclusions}

\section*{Link}
The code is available at \href{https://github.com/Sproc01/GT_PrimeComposite.git}{\textit{Repository}}

\section*{Acknowledgment}
Luciano Murrone that presented to us this game.

\section*{References}
\begin{itemize}
    \item L. Badia, T. Marchioro, Game theory - A handbook of problems and exercises, Esculapio, 2022
    \item S. Tadelis, Game Theory: an introduction. Princeton, 2013.
\end{itemize}


\end{document}

