\section{Simulation}\label{section:Simulation}
We now cover the simulation work that we have done in order to analyze the fairness of the game and the performance of the proposed practical strategies.

For the sake of clarity, in this section we are going to refer to a generic player 1 as P1 and to player 2 as P2 for simplicity.

In order to understand if there is an inherent advantage in going first or second, we run several simulations and compare the outcomes of the games under all the combinations of two strategies from the ones explained in section \ref{section: Strategies}. In particular, we consider two cases:
\begin{itemize}
	\item General case: whoever starts between P1 and P2 is decided by which player gets the card 2 in its hand.
	\item P1 always starts: player P1 always gets the hand containing the 2, thus playing first.
\end{itemize}
To achieve our objective, we first generate $n$ pairs of random hands, one for each player. Then for each pair of hands, we simulate the game on every possible combination of two strategies from Section \ref{section: Strategies}.
We make the simplifying assumption of players sticking to their selected strategy. Obviously, this abstracts us from the human-playing scenario; however, it is an abstraction without loss of generality, since our focus is in finding evidence of an intrinsic unfairness of the game that must remove itself of any human-like factors.

Specifically, the simulations have been run on Google Colab with default configuration\footnote{Intel(R) Xeon(R) CPU @ 2.20GHz, 13 GB of RAM}, for a total of $n = 10000$ simulations of random hands for all possible combinations of strategies. This number of runs has been chosen in order to guarantee both a high enough sample size and a feasible computational time.

\input{sections/Outcomes.tex}

\input{sections/Scores.tex}
